---
title: "Untitled"
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE}
suppressPackageStartupMessages(require(timeSeries))
suppressPackageStartupMessages(require(fPortfolio)) # may also require installing the package require(slam)
suppressPackageStartupMessages(require(quantmod))
suppressPackageStartupMessages(require(tidyquant))
suppressPackageStartupMessages(require(XLConnect))
suppressPackageStartupMessages(require(readr))
```

```{r}
library(quantmod)

Monthly.Return.Latest <- NULL
#using for loop we create ererytime a matrix for the monthly returns for every ticker in the 10 stocks we choose in every state of j were j is the state of every month anf then select the date of the last traidng day of the month which is the monhly return of that stock
for(k in 1:10) {
  Monthly.Return.Latest <- cbind(Monthly.Return.Latest, monthlyReturn(ClosingPricesRead[,k])) # creating a matrix with all the monthly returns for each ticker
}
colnames(Monthly.Return.Latest) <- TickerList.New
Stock.Monthly.Return <- tail(Monthly.Return.Latest,1) #select the return for the particular date we need

Proportionate.Monthly.Return <- Stock.Monthly.Return*Allocation.New

Portfolio.Investment <- (sum(Proportionate.Monthly.Return) + 1)*Portfolio.Investment

Wealth <- Portfolio.Investment
# Wealth in proportion

print(Wealth)
```

```{r}
TickerList.Old <- TickerList.New
Allocation.Old <- Allocation.New
```

```{r message=FALSE, warning=FALSE}
library(tidyquant)
a <- tq_index("SP500") 

TickerList.Latest <- a[1:150,1]

# Latest S&P 150. 150 so that we can check in the code for errors about tickers.
```

```{r message=FALSE, warning=FALSE}
library(quantmod)


Error.Check <- lapply(TickerList.Latest, function(x){try(getSymbols(x),silent=TRUE)})
# This checks for each ticker if there is an error and prints a list of 150 with the ticker or an error message.

TickerList4 <- NULL
counter = 1
for (i in 1:150) {
  if(Error.Check[[i]] == TickerList.Latest[i]) {
  TickerList4[counter] <- TickerList.Latest[i]
  counter = counter + 1
  }
  
}
# Creating a new list without the tickers that has errors

TickerList4 <- TickerList4[1:100]
# S&P 100
```

```{r}

currentDate <- Sys.Date()
# Latest date

sopm <- currentDate - days(day(currentDate))
date <- sopm - days(day(sopm) - 1)
# First day of the previous month

ClosingPricesRead <- NULL
for (Ticker in TickerList4){
  
  ClosingPricesRead <- cbind(ClosingPricesRead, getSymbols(Ticker, from=date, verbose=FALSE, auto.assign=FALSE)[,6])

}
# Adjusted closing prices for the last month.



# ClosingPricesRead <- tail(ClosingPricesRead,10)
# If we want to calculate sharpe ratio for the last 10 days we'll use the line above.

```

```{r}
Returns <- as.xts((tail(ClosingPricesRead,-1) / as.numeric(head(ClosingPricesRead,-1)))-1)
# Daily returns
```

```{r}
numtick <- length(TickerList4)

TickerRet <- NULL
TickerStd <- NULL 
TickerSharpe <- NULL

for (i in 1:numtick){
  TickerRet <- cbind(TickerRet, mean(Returns[,i]))
  TickerStd <- cbind(TickerStd, sd(as.numeric(Returns[,i])))
  TickerSharpe <- cbind(TickerSharpe, (TickerRet[i]*252)/(TickerStd[i]*sqrt(252)))
                        }
```

```{r}
TickerInfo <- t(rbind(TickerRet, TickerStd, TickerSharpe))

rownames(TickerInfo) <- TickerList4
colnames(TickerInfo) <- c("Mean", "StD", "Sharpe")
```

```{r}
TickerInfo <- as.data.frame(TickerInfo)
TickerInfo <- TickerInfo[order(-TickerInfo$Sharpe),]
TopTickerSharpe <- paste(rownames(head(TickerInfo, 10)), sep = "")
print(TopTickerSharpe)

```

```{r}
TickerList.New <- TopTickerSharpe
```
# read closing prices from Yahoo keeping only the closing prices
```{r}
ClosingPricesRead <- NULL
for (Ticker in TickerList.New){
  ClosingPricesRead <- cbind(ClosingPricesRead,
                             getSymbols(Ticker, from=date, verbose=FALSE, auto.assign=FALSE)[,6]) # [,6] = keep the adjusted prices
}
```
# keep only the dates that have closing prices for all tickers
```{r}
ClosingPrices <- ClosingPricesRead[apply(ClosingPricesRead,1,function(x) all(!is.na(x))),]
```
# convert prices to daily returns
```{r}
library(timeSeries)

returns <- as.timeSeries((tail(ClosingPrices,-1) / as.numeric(head(ClosingPrices,-1)))-1)
```
# calculate the efficient frontier
```{r}
library(fPortfolio)

Frontier <- portfolioFrontier(returns)
```

```{r}
plot(Frontier,1) # can also call the plot routine so it only plots the frontier: plot(Frontier,1)
```

# execute the next commands to plot annualized returns and risk
# convert from daily to annual returns and risk for points on the efficient frontier

```{r}
riskReturnPoints <- frontierPoints(Frontier) # get risk and return values for points on the efficient frontier
annualizedPoints <- data.frame(targetRisk=riskReturnPoints[, "targetRisk"] * sqrt(252),
                               targetReturn=riskReturnPoints[,"targetReturn"] * 252)
```
# plot Sharpe ratios for each point on the efficient frontier
```{r}
riskFreeRate <- 0
plot((annualizedPoints[,"targetReturn"] - riskFreeRate) / annualizedPoints[,"targetRisk"], xlab="point on efficient frontier", ylab="Sharpe ratio")
```

```{r}
portfolioSharpeRatio <- (annualizedPoints[,"targetReturn"] - riskFreeRate)/annualizedPoints[,"targetRisk"]

bestindex <- which(portfolioSharpeRatio==max(portfolioSharpeRatio))
```
# plot the allocation to each stock for each point on the efficient frontier
# weightsPlot(Frontier)
```{r}
allocations <- getWeights(Frontier@portfolio) # get allocations for each instrument for each point on the efficient frontier
colnames(allocations) <- TickerList.New
barplot(t(allocations), col=rainbow(ncol(allocations)+2), legend=colnames(allocations), names.arg = c(1:50))
```
# final decision of allocations with target return and target volatility
```{r}

Allocation.New <- allocations[bestindex,]

Allocation.New
```

```{r setup, include=FALSE}

Consecutive.Stocks.Latest <- NULL

for(i in 1:10){
  if(is.element(TickerList.Old[i],TickerList.New) == TRUE){
    Consecutive.Stocks.Latest <- cbind(Consecutive.Stocks.Latest,TickerList.Old[i])
  }
}

```

```{r}
c <- 0

  if (length(Consecutive.Stocks.Latest) > 0) { # If statement checks if there are retained stocks. length(...) is the number of stocks that are retained.
    
    
    for (j in 1:length(Consecutive.Stocks.Latest)) {
      b <- Consecutive.Stocks.Latest[j]
      c <- c + min(Allocation.Old[b],Allocation.New[b])
    }
    # min is the proportion of the stocks that are not bought or sold and hence transaction costs are not relevant for     that proportion of stocks.
    # At the end c will be the total proportion of stocks not bought or sold between the consecutive months.
  

  } 

Retained.Portfolio.Stocks.Latest <- c
```

```{r}

Wealth <- Wealth*(1-Retained.Portfolio.Stocks.Latest)*0.9911 + Wealth*Retained.Portfolio.Stocks.Latest

  # a + b
  # a = Wealth times proportion of stocks bought/sold times (1 - transaction costs).
  # Transaction costs = 0.89 % or 0.0089
  # b = Wealth times proportion of stocks not bought/sold, hence no transaction costs.

print(Wealth)
```