
```{r message=FALSE, warning=FALSE, include=FALSE}

install.packages("tidyquant")
install.packages("XLConnect")
install.packages("readr")
install.packages("timeSeries")
install.packages("fPortfolio")
install.packages("quantmod")


```

```{r message=FALSE, warning=FALSE}
library(tidyquant)
library(quantmod)
library(timeSeries)
library(fPortfolio)

```

```{r}
Portfolio.Investment <- 1
# Initial investment available
```

```{r message=FALSE, warning=FALSE}

a <- tq_index("SP500") 

TickerList.Latest <- a[1:150,1]

# Latest S&P 150. 150 so that we can check in the code for errors about tickers.
```



```{r message=FALSE, warning=FALSE}



Error.Check <- lapply(TickerList.Latest, function(x){try(getSymbols(x),silent=TRUE)})
# This checks for each ticker if there is an error and prints a list of 150 with the ticker or an error message.

TickerList4 <- NULL
counter = 1
for (i in 1:150) {
  if(Error.Check[[i]] == TickerList.Latest[i]) {
  TickerList4[counter] <- TickerList.Latest[i]
  counter = counter + 1
  }
  
}
# Creating a new list without the tickers that has errors

TickerList4 <- TickerList4[1:100]
# S&P 100
```

```{r}

currentDate <- Sys.Date()
# Latest date

sopm <- currentDate - days(day(currentDate))
date <- sopm - days(day(sopm) - 1)
# First day of the previous month

ClosingPricesRead <- NULL
for (Ticker in TickerList4){
  
  ClosingPricesRead <- cbind(ClosingPricesRead, getSymbols(Ticker, from=date, verbose=FALSE, auto.assign=FALSE)[,6])

}
# Adjusted closing prices for the last month.
```

```{r}
Returns <- as.xts((tail(ClosingPricesRead,-1) / as.numeric(head(ClosingPricesRead,-1)))-1)
# Daily returns
```

```{r}
numtick <- length(TickerList4)

TickerRet <- NULL
TickerStd <- NULL 
TickerSharpe <- NULL

for (i in 1:numtick){
  TickerRet <- cbind(TickerRet, mean(Returns[,i]))
  TickerStd <- cbind(TickerStd, sd(as.numeric(Returns[,i])))
  TickerSharpe <- cbind(TickerSharpe, (TickerRet[i]*252)/(TickerStd[i]*sqrt(252)))
                        }
```

```{r}
TickerInfo <- t(rbind(TickerRet, TickerStd, TickerSharpe))

rownames(TickerInfo) <- TickerList4
colnames(TickerInfo) <- c("Mean", "StD", "Sharpe")
```

```{r}
TickerInfo <- as.data.frame(TickerInfo)
TickerInfo <- TickerInfo[order(-TickerInfo$Sharpe),]
TopTickerSharpe <- paste(rownames(head(TickerInfo, 10)), sep = "")
print(TopTickerSharpe)

```

```{r}
TickerList.New <- TopTickerSharpe
```
# read closing prices from Yahoo keeping only the closing prices
```{r}
ClosingPricesRead <- NULL
for (Ticker in TickerList.New){
  ClosingPricesRead <- cbind(ClosingPricesRead,
                             getSymbols(Ticker, from=date, verbose=FALSE, auto.assign=FALSE)[,6]) # [,6] = keep the adjusted prices
}
```
# keep only the dates that have closing prices for all tickers
```{r}
ClosingPrices <- ClosingPricesRead[apply(ClosingPricesRead,1,function(x) all(!is.na(x))),]
```
# convert prices to daily returns
```{r}
returns <- as.timeSeries((tail(ClosingPrices,-1) / as.numeric(head(ClosingPrices,-1)))-1)
```
# calculate the efficient frontier
```{r}
Frontier <- portfolioFrontier(returns)
```

```{r}
plot(Frontier,1) # can also call the plot routine so it only plots the frontier: plot(Frontier,1)
```

# execute the next commands to plot annualized returns and risk
# convert from daily to annual returns and risk for points on the efficient frontier

```{r}
riskReturnPoints <- frontierPoints(Frontier) # get risk and return values for points on the efficient frontier
annualizedPoints <- data.frame(targetRisk=riskReturnPoints[, "targetRisk"] * sqrt(252),
                               targetReturn=riskReturnPoints[,"targetReturn"] * 252)

```
# plot Sharpe ratios for each point on the efficient frontier
```{r}
riskFreeRate <- 0
plot((annualizedPoints[,"targetReturn"] - riskFreeRate) / annualizedPoints[,"targetRisk"], xlab="point on efficient frontier", ylab="Sharpe ratio")
```

```{r}
portfolioSharpeRatio <- (annualizedPoints[,"targetReturn"] - riskFreeRate)/annualizedPoints[,"targetRisk"]

bestindex <- which(portfolioSharpeRatio==max(portfolioSharpeRatio))
```
# plot the allocation to each stock for each point on the efficient frontier
# weightsPlot(Frontier)
```{r}
allocations <- getWeights(Frontier@portfolio) # get allocations for each instrument for each point on the efficient frontier
colnames(allocations) <- TickerList.New
barplot(t(allocations), col=rainbow(ncol(allocations)+2), legend=colnames(allocations), names.arg = c(1:50))
```
# final decision of allocations with target return and target volatility
```{r}

Allocation.New <- allocations[bestindex,]


Portfolio.Investment <- Portfolio.Investment*(1-0.0089)
# 0.0089 is the transaction costs. Since we are buying all the stocks, transaction costs need to be paid for all stocks.

Wealth <- Portfolio.Investment

Allocation.New
```










